### 2018-01-30 includes/introduction.tex
add section labels; remove manual spacing; fix sectioning

        \begin{enumerate}
            \item \textbf{The \fuzzer{} tool}: We describe a modular fuzzer which can transform and generate \smtfull{} string and regex problems. We briefly document its components and modular architecture. We provide example use cases to demonstrate its usefulness as an exploratory tool for validating solvers. We additionally detail its regex generation and transformation capabilities.
            \item \textbf{A repository of \smtfull{} problems}: We present a repository of \smtfull{} string and regex problem suites we generated using \fuzzer{}. We demonstrate the usefulness of these suites by revealing specific defects they helped uncover and fix in \us{}.
            \item \textbf{Experimental Results}: We compare \theSolvers{} on the \fuzzer{} suites and selectively present the experimental result on \theSuites{}. We highlighted these suites because they uniquely made some solvers perform poorly, but not others.
            \item \textbf{Analysis}: We analyze our experimental results by inspecting the execution traces of the solvers on the given problems. For \us{}, we pinpoint algorithmic limitations that cause poor performance. For other solvers, we draw superficial conclusions based solely on the execution traces, and invite their authors to conduct further analysis.
        \end{enumerate}

>>>>

        \begin{enumerate}
            \item \textbf{The \fuzzer{} tool}: We describe in Section~\ref{sec:fuzzer} a modular fuzzer which can transform and generate \smtfull{} string and regex problems. We briefly document its components and modular architecture. We provide example use cases to demonstrate its usefulness as an exploratory tool for validating solvers. We additionally detail its regex generation and transformation capabilities.
            \item \textbf{A repository of \smtfull{} problems}: We present a repository of \smtfull{} string and regex problem suites we generated using \fuzzer{} in Section~\ref{sec:problems}. We demonstrate the usefulness of these suites by revealing specific defects they helped uncover and fix in \us{}.
            \item \textbf{Experimental Results}: We compare \theSolvers{} on the \fuzzer{} suites and selectively present the experimental result on \theSuites{} in Section~\ref{sec:data}. We highlighted these suites because they uniquely made some solvers perform poorly, but not others.
            \item \textbf{Analysis}: We analyze our experimental results in Section~\ref{sec:analysis} by inspecting the execution traces of the solvers on the given problems. For \us{}, we pinpoint algorithmic limitations that cause poor performance. For other solvers, we draw superficial conclusions based solely on the execution traces, and invite their authors to conduct further analysis.
        \end{enumerate}

### 2018-01-30 includes/problems.tex
add section labels; remove manual spacing; fix sectioning

\section{Problem Suites}
\label{sec:problems}
\vspace{-0.1in}

@@

\subsection{Generated suite}
\vspace{-0.1in}
    We generated several suites of string and regex problems using \fuzzer{}\footnote{For review anonymity, we removed the link to the source code and the generated suites. They will be provided separately in the artifact submission.}. Table~\ref{tbl:generated} describes the suite \texttt{generated} by \generator{}.

@@

\vspace{-0.2in}
\subsection{Transformed suite}
\vspace{-0.1in}
    The \texttt{transformed} suite contains benchmarks derived from existing seed problems by iteratively applying \transformer{}. Table~\ref{tbl:transformed} shows the overview. Every problem in the suite is named according to its seed and the transformations it undertook. For example, input \texttt{seed-fuzz-graft.smt2} was transformed by applying \texttt{fuzz} and then \texttt{graft} from \texttt{seed.smt2}.

>>>>

\section{Problem Suites}
\label{sec:problems}

@@

\subsection{Generated suite}

    We generated several suites of string and regex problems using \fuzzer{}\footnote{For review anonymity, we removed the link to the source code and the generated suites. They will be provided separately in the artifact submission.}. Table~\ref{tbl:generated} describes the suite \texttt{generated} by \generator{}.

@@

\subsection{Transformed suite}

    The \texttt{transformed} suite contains benchmarks derived from existing seed problems by iteratively applying \transformer{}. Table~\ref{tbl:transformed} shows the overview. Every problem in the suite is named according to its seed and the transformations it undertook. For example, input \texttt{seed-fuzz-graft.smt2} was transformed by applying \texttt{fuzz} and then \texttt{graft} from \texttt{seed.smt2}.
